### 2016-01-25 inputs/materials_and_methods.tex
tetraploid explained

A further quality filter, implemented through ad-hoc Python scripts, removed heterozygous loci with less than 4 and homozygous loci with less than 11 aligned reads. A similar filtering was performed in \cite{Rocher_validation_2015} using less restrictive thresholds.

. Alfalfa is an autotetraploid plant species and can therefore present three different heterozygous genotypes: AAAB, AABB and ABBB. Following \cite{li_saturated_2014} and \cite{li_genomic_2015}, these were all considered diploid heterozygotes (i.e. AB), while the two homozygous genotypes (AAAA and BBBB) were considered diploid homozygotes (i.e., AA or BB).\\

>>>>

A further quality filter, implemented through ad-hoc Python scripts, removed heterozygous loci with less than 4 and homozygous loci with less than 11 aligned reads. A similar filtering was performed in \cite{Rocher_validation_2015} using less restrictive thresholds. Alfalfa is an autotetraploid plant species and can therefore present three different heterozygous genotypes: AAAB, AABB and ABBB. Sequencing depth in this study was not sufficient for accurate tetraploid allelic dosage, but following \cite{li_saturated_2014} and \cite{li_genomic_2015} reliable genotype calls based on diploid allelic dosage were obtained considering diploid heterozygotes (i.e. AB), while the two homozygous genotypes (AAAA and BBBB) were considered diploid homozygotes (i.e., AA or BB).
